The Practical Application of Computerised Multistage Tests

### 2021-02-24 article.Rmd
Use proper caption for MIF graphs

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="I(θ)")
```
You can see that the maximum information point Module A is pretty close to $\theta = 0$.

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="I(θ)") +
  geom_vline(xintercept = 0.81, linetype="dotted")
```
Here we can see that there is point of intersection between modules B and C. This suggests, that candidates who have a $\hat\theta < 0.81$ in Module A should be routed to Module B, and all others routed to Module C.

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="I(θ)")

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="I(θ)")
```

>>>>

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="θ", y="I(θ)")
```
You can see that the maximum information point Module A is pretty close to $\theta = 0$.

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="θ", y="I(θ)") +
  geom_vline(xintercept = 0.81, linetype="dotted")
```
Here we can see that there is point of intersection between modules B and C. This suggests, that candidates who have a $\hat\theta < 0.81$ in Module A should be routed to Module B, and all others routed to Module C.

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="θ", y="I(θ)")

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="θ", y="I(θ)")
```
